\section{Communication Strategy}

Ensuring that the system we design and prototype meets customer needs is a central focus at each team meeting. In our first meeting, we established a communication strategy which we leveraged in order to gather requirements from the customer. We continue to use this strategy to keep the customer updated with any new ideas, or modifications to existing plans. Namely, we defined that the Customer Relations Manager (PK) is responsible for soliciting any queries, updates or requests. The customer relations manager keeps other team members informed of any intended communications using a dedicated channel in our team coordination tool, Slack. This gives team members the opportunity to review pending communications -- checking them for clarity and relevance to the project. The customer relations manager is also responsible for arranging and leading any face-to-face meetings with the client.

Our initial contact with the customer took place during the first project briefing. In this briefing, we discussed the issues facing the maritime industry and discussed some potential areas on which our solution should be focused. We noted the customer’s priorities, and they shared several pressing issues to which they assign a particular importance. We evaluated potential solutions, and how feasible it would be to develop them in the timescales available. The customer expressed interest in several of our initial ideas, and notably in the concept of autonomous cargo. After further discussion with the client, the team decided to pursue the different, but related concept of offshore ports paired with autonomous shuttle ships.

In a subsequent team meeting, we discussed the our proposed solution further in order to establish its viability. We drafted and sent an email to the customer to gauge their interest and enthusiasm, and to solicit feedback for our initial design. The customer responded positively, giving us confidence in our idea, and allowing us to proceed with a more detailed design concept. In the next assessment phase, we intend to work closely with the customer to refine our prototype and system design.
